
# Navigate the network

##  {.sidebar data-width="300"}

#### Controls

Pick a protein to display its interactions:

```{r, cache = FALSE}
selectInput(inputId='centerGene',choices=all_nodes$GeneName,label=NULL,selected = "STK11", multiple = F)
infoGene <- reactive({na.omit(c(input$selectGene,input$centerGene)[[1]])})
``` 
Use mouse controls to pan and zoom. \
Click on a node to display information. \
Double-click on a node to recenter graph. 


#### Selected node `r renderText(infoGene())`
```{r,cache=FALSE}
  renderUI({render_gene_info(infoGene())})
```


#### Legend {data-height="210"}
Node colors indicate kinase-group.
```{r, cache=FALSE}
# legend_nodes <- data.frame(
#   id=1:length(group_names),
#   label = group_names,
#   color = group_colors,
#   size = 20
# )
# legend_edges <- data.frame()
# visNetwork(legend_nodes,legend_edges,width="90%") %>%
#   visNodes(font=list(size=30)) %>%
#   visOptions(width="90%",height="200")
```
#### Export

```{r, cache=FALSE}
  actionButton("export","Export")
```

## Main Panel
#### Kinase-substrate interactions of `r renderText(input$centerGene)`
###  {}
```{r, cache=FALSE}
#renderText(input$centerGene)
nodes <- data.frame(id=1:10)
edges <- data.frame(from=sample(1:10,8),to=sample(1:10,8))
renderVisNetwork(nodes,edges,width="100%")
```


