
# Visualize gene sets
##  {.sidebar data-width="300"}
#### Controls
To visualize a pre-loaded gene set, select a pathway category:

```{r, cache = FALSE}
selectInput(inputId='pathwayCategory',label=NULL,choices=pathway_categories,selected=default_pathway_category)
selectInput(inputId='pathwayName',label=NULL,choices=pathway_choices[[default_pathway_category]] %>% pull(Term))
observeEvent(input$pathwayCategory,{
  updateSelectInput(inputId='pathwayName',choices = pathway_choices[[input$pathwayCategory]] %>% pull(Term))
})
proteinList <- reactive({get_pathway_genes(input$pathwayCategory, input$pathwayName)})
infoProtein <- reactive({na.omit(c(input$selectProtein,proteinList()[[1]])[[1]])})
```
Use mouse controls to pan and zoom. \
Click on a node to display information. \
Double-click on a node, then click on "Navigate the network" to view its interactions.

#### Selected node `r renderText(infoProtein())`

```{r, cache=FALSE}
  renderUI({
    info <- get_protein_info(infoProtein())
    unip_url <- 'https://www.uniprot.org/uniprotkb/%s/entry'
    L1 <-  list(tags$b(info$fullname),tags$br())
    L2 <- list('UniProt: ',tags$a(info$uniprot,href= sprintf(unip_url,info$uniprot)), tags$br())
    L3 <- list()
    for(x in info$remaining) {
      L3 <- c(L3,list(x,tags$br()))
    }
    tagList(L1,L2,L3)
  })
```
#### Legend {data-height="210"}
Node colors indicate kinase-group.
```{r, cache=FALSE}
legend_nodes <- data.frame(
  id=1:length(group_names),
  label = group_names,
  color = group_colors,
  size = 20
)
legend_edges <- data.frame()
visNetwork(legend_nodes,legend_edges,width="90%") %>%
  visNodes(font=list(size=30)) %>%
  visOptions(width="90%",height="200")
```

## Main Panel 
#### Kinase-substrate interactions of `r renderText(input$pathwayName)`
### {data-height="800"}

```{r,cache = FALSE}

renderVisNetwork({
 subg1 = induced_subgraph(ks_ig,proteinList())
 V(subg1)$color = sapply(V(subg1)$name,get_color)
 data <- toVisNetworkData(subg1)
 visNetwork(nodes=data$nodes,edges=data$edges,physics=F) %>%
   visIgraphLayout() %>%
   visOptions(highlightNearest = list(enabled = T, hover = T)) %>%
   visNodes(size=20,font=list(size=30)) %>%
   visEdges(arrows = "to",smooth=F) %>%
   visEvents(doubleClick = "function(nodes) {Shiny.onInputChange('nextCenterProtein', nodes.nodes);}") %>%
   visEvents(click = "function(nodes){Shiny.onInputChange('selectProtein', nodes.nodes);}") 
})

```